Searching 21-cm Absorption Systems in Chinese Radio Telescopes

### 2016-11-15 ms_21cm.tex
add refs

\newcommand{\cpm}{{\small CUBEP$^3$M}}
\newcommand{\smjustify}{\hspace{-0.1cm}}
\def\smwidth{0.48\textwidth}
\def\smhwidth{0.48\textwidth}

@@

\author{
Hao-Ran Yu\inst{1,2},
Ue-Li Pen\inst{2,3,4,5},
Tong-Jie Zhang\inst{6},
Di Li\inst{7,8},
Xuelei Chen\inst{9}
}

@@

>>>>

\newcommand{\diff}{{\rm d}}
\newcommand{\cpm}{{\small CUBEP$^3$M}}
\newcommand{\smjustify}{\hspace{-0.1cm}}
\def\smwidth{0.48\textwidth}
\def\smhwidth{0.48\textwidth}

@@

\author{
Hao-Ran Yu\inst{1,2},
Ue-Li Pen\inst{2,3,4,5},
Tong-Jie Zhang\inst{6},
Di Li\inst{7,8} and
Xuelei Chen\inst{9}
}

@@

FAST \citep{2016RaSc...51.1060L} and Tianlai \citep{2012IJMPS..12..256C}. Direct measurement of cosmic acceleration
\citep{2012ApJ...761L..26D}, and its proposal
on CHIME \citep{2014PhRvL.113d1303Y}

Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.

NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.

Recent studies show that the number density of absorbers to be $\diff N/\diff z\sim 0.45$
\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}.

Recent discoveries of 21-cm absorption systems have about $20\%$ fractional depth
\citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z}.
